---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rgugik

<!-- badges: start -->
[![R build status](https://github.com/kadyb/rgugik/workflows/rcmdcheck/badge.svg)](https://github.com/kadyb/rgugik/actions)
<!-- badges: end -->

**rgugik** is an R package for downloading open data from resources of [Polish Head Office of Geodesy and Cartography](http://www.gugik.gov.pl).
Currently you can download:

  - [Orthophotomaps](http://www.gugik.gov.pl/pzgik/zamow-dane/ortofotomapa)
  - [Digital Terrain Models](http://www.gugik.gov.pl/pzgik/zamow-dane/numeryczny-model-terenu) as XYZ vector points with 1 m resolution
  - Digital Terrain Models as XYZ text files with 100 m resolution for entire voivodeships
  - [General Geographic Database](http://www.gugik.gov.pl/pzgik/zamow-dane/baza-danych-obiektow-ogolnogeograficznych)
  - [State Register of Geographical Names](http://www.gugik.gov.pl/pzgik/zamow-dane/panstwowy-rejestr-nazw-geograficznych)
  - Location (geometry) of cadastral parcels using TERYT (parcel ID) or coordinates
  - 3D models of buildings (LOD1, LOD2)

It is also possible to geocode addresses or objects using the `geocode` function.

**Corresponding functions**

```{r echo=FALSE}
ds_pl = c("Ortofotomapa",
          "Numeryczny Model Terenu",
          "Baza Danych Obiektów Ogólnogeograficznych",
          "Państwowy Rejestr Nazw Geograficznych",
          "Lokalizacja działek katastralnych",
          "Modele 3D budynków")

ds_en = c("Orthophotomap",
          "Digital Terrain Models",
          "General Geographic Database",
          "State Register of Geographical Names",
          "Location of cadastral parcels",
          "3D models of buildings")

fun = c("orto_request, orto_download",
        "pointDTM_get, pointDTM100_download",
        "geodb_download",
        "geonames_download",
        "parcel_get",
        "models3D_download")

input = c("polygon",
          "polygon, voivodeship (TERC)",
          "voivodeship (TERC)",
          "place, object",
          "parcel ID, coordinates",
          "county (TERYT)")

df = data.frame(ds_pl, ds_en, fun, input)
colnames(df) = c("Dastaset PL", "Dataset EN", "Function", "Input")

knitr::kable(df)
```

## Installation

<!-- You can install the released version of rgugik from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rgugik") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com) with:

```{r message=FALSE, warning=FALSE, eval=FALSE}
# install.packages("remotes")
remotes::install_github("kadyb/rgugik")
```

## Usage

### Ortophotomap
  
- `orto_request()` - returns a data frame with metadata and links to the orthoimages in a given polygon
- `orto_download()` - downloads orthoimages based on the data frame obtained using the `orto_request()` function
  
```{r message=FALSE, warning=FALSE}
library(rgugik)
library(sf)
library(raster)

polygon_path = system.file("datasets/search_area.gpkg", package = "rgugik")
polygon = read_sf(polygon_path)

req_df = orto_request(polygon)

# show metadata and download the first image only
t(req_df[1, ])
orto_download(req_df[1, ])

img = brick("41_3756_N-33-130-D-b-2-3.tif")
plotRGB(img)
```

```{r echo=FALSE, message=FALSE}
invisible(file.remove("41_3756_N-33-130-D-b-2-3.tif"))
```

### DTM (as XYZ)

```{r}
library(rgugik)
library(sf)

polygon_path = system.file("datasets/search_area.gpkg", package = "rgugik")
polygon = read_sf(polygon_path)

DTM = pointDTM_get(polygon)

plot(DTM, pal = terrain.colors, pch = 20, main = "Elevation [m]")
```

## Acknowledgment

<!-- please add the content here-->

## Contribution

Contributions to this package are welcome. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [an issue](https://github.com/kadyb/rgugik/issues).

## Related project

If you don't feel familiar with R, there are similar tools to [QGIS](https://www.qgis.org) in the [EnviroSolutions](https://github.com/envirosolutionspl) repository.
