---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rgugik

<!-- badges: start -->
<!-- badges: end -->

**rgugik** is an R package for downloading open data from resources of [Polish Head Office of Geodesy and Cartography](http://www.gugik.gov.pl/).
Currently you can download:

  - [Orthophotomaps](http://www.gugik.gov.pl/pzgik/zamow-dane/ortofotomapa)
  - [Digital Terrain Models](http://www.gugik.gov.pl/pzgik/zamow-dane/numeryczny-model-terenu) as XYZ vector points with 1 m resolution
  - Digital Terrain Models as XYZ text files with 100 m resolution for entire voivodeships
  - [General Geographic Database](http://www.gugik.gov.pl/pzgik/zamow-dane/baza-danych-obiektow-ogolnogeograficznych)
  - [State Register of Geographical Names](http://www.gugik.gov.pl/pzgik/zamow-dane/panstwowy-rejestr-nazw-geograficznych)
  - Location of cadastral parcels using TERYT (parcel ID) or coordinates
  - 3D models of buildings (LOD1, LOD2)

## Installation

<!-- You can install the released version of rgugik from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("rgugik") -->
<!-- ``` -->

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("kadyb/rgugik")
```

## Usage

### Ortophotomap
  
- `orto_request()` - returns a data frame with metadata and links to the orthoimages in a given polygon
- `orto_download()` - downloads orthoimages based on the data frame obtained using the `orto_request()` function
  
```{r}
library(rgugik)
library(sf)
library(raster)
polygon_path = system.file("datasets/search_area.gpkg", package = "rgugik")
polygon = read_sf(polygon_path)
req_df = orto_request(polygon)
str(req_df)
orto_download(req_df[1, ]) # download the first image only
img = brick("41_3756_N-33-130-D-b-2-3.tif")
plotRGB(img)
```

```{r, echo=FALSE, message=FALSE}
invisible(file.remove("41_3756_N-33-130-D-b-2-3.tif"))
```

### DTM (as XYZ)

```{r, eval=FALSE}
library(rgugik)
library(sf)
polygon_path = system.file("datasets/search_area.gpkg", package = "rgugik")
polygon = read_sf(polygon_path)
DTM = pointDTM_get(polygon)
summary(DTM$elev)
plot(DTM, pal = terrain.colors, pch = 20, main = "Elevation [m]")
```

## Acknowledgment

<!-- please add the content here-->

## Contribution

Contributions to this package are welcome. 
The preferred method of contribution is through a GitHub pull request. 
Feel also free to contact us by creating [an issue](https://github.com/kadyb/rgugik/issues).
