---
title: "General Geographic Database"
date: "`r Sys.Date()`"
output: github_document
---

## Baza Danych Obiektów Ogólnogeograficznych (BDOO)<br>General Geographic Database


### Main categories of data

```{r include=FALSE}
main_abbre = c(
  "OT",
  "AD",
  "BU",
  "PT",
  "TC",
  "SW",
  "SK"
  )

main_pl = c(
  "Obiekt topograficzny",
  "Administracja",
  "Budowle",
  "Pokrycie terenu",
  "Tereny chronione",
  "Sieć wodna",
  "Sieć komunikacyjna"
  )

main_en = c(
  "Topographic object",
  "Administration",
  "Buildings",
  "Land cover",
  "Protected areas",
  "Water network",
  "Communication network"
  )

df_main = data.frame(ABBRE = main_abbre, POLISH = main_pl, ENGLISH = main_en)
```

```{r echo=FALSE}
knitr::kable(df_main)
```


### Second level of categories (names of vector layers)

```{r include=FALSE}
abbre = c(
  "ADJA",
  "ADMS",
  "BUHD",
  "BUIN",
  "BUIT",
  "BUUO",
  "BUWT",
  "BUZM",
  "KUIK",
  "KUKO",
  "KUPG",
  "KUSC",
  "KUSK",
  "OIKM",
  "OIMK",
  "PTGN",
  "PTLZ",
  "PTNZ",
  "PTPL",
  "PTRK",
  "PTSO",
  "PTTR",
  "PTUT",
  "PTWP",
  "PTWZ",
  "PTZB",
  "SKDR",
  "SKPP",
  "SKRW",
  "SKTR",
  "SULN",
  "SWKN",
  "SWRM",
  "SWRS",
  "TCON",
  "TCPK",
  "TCPN",
  "TCRZ"
  )

pl = c(
  "Jednostka podziału administracyjnego",
  "Punkt główny miejscowości",
  "Budowla hydrotechniczna",
  "Budowla inżynierska",
  "Inne urządzenia techniczne",
  "Umocnienie drogowe, kolejowe i wodne",
  "Wysoka budowla techniczna",
  "Budowla ziemna",
  "Inny kompleks użytkowania terenu",
  "Kompleks komunikacyjny",
  "Kompleks przemysłowo-gospodarczy",
  "Kompleks sakralny i cmentarz",
  "Kompleks sportowo rekreacyjny",
  "Obiekt związany z komunikacją",
  "Mokradła",
  "Teren gruntów nieużytkowanych",
  "Teren leśny lub zadrzewiony",
  "Inny teren niezabudowany",
  "Teren placów",
  "Teren roślinności krzewiastej",
  "Teren składowania odpadów",
  "Teren roślinności trawiastej lub upraw rolnych",
  "Teren upraw trwałych",
  "Woda powierzchniowa",
  "Tereny zwałowisk i wyrobisk",
  "Zabudowa",
  "Droga",
  "Przeprawa",
  "Rondo lub węzeł drogowy",
  "Tor lub zespół torów",
  "Linia napowietrzna",
  "Kanał",
  "Rów melioracyjny",
  "Rzeka strumień",
  "Obszar Natura 2000",
  "Parki Krajobrazowe",
  "Parki Narodowe",
  "Rezerwaty"
  )

en = c(
  "Administrative subdivision",
  "Focal point of the town",
  "Hydraulic structure",
  "Engineering construction",
  "Other technical devices",
  "Road, rail and waterway reinforcements",
  "High technical construction",
  "Earth structure",
  "Other land use complex",
  "Communication complex",
  "Industrial and economic complex",
  "Religious complex and cemetery",
  "Sports and recreation complex",
  "Object related to communication",
  "Wetlands",
  "Unused lands area",
  "Forest or wooded area",
  "Other undeveloped area",
  "Squares area",
  "Shrubland area",
  "Landfill area",
  "Grassland or agricultural area",
  "Permanent crops area",
  "Surface water",
  "Heap and excavation areas",
  "Buildings",
  "Road",
  "Passage",
  "Roundabout or road junction",
  "Track or track set",
  "Overhead line",
  "Channel",
  "Drainage ditch",
  "River stream",
  "Natura 2000 area",
  "Landscape parks",
  "National park",
  "Nature reserve"
  )

df = data.frame(ABBRE = abbre, POLISH = pl, ENGLISH = en)
```

```{r echo=FALSE}
knitr::kable(df)
```

The last character in a vector layer name means:
  
  + **P** - point
  + **L** - line
  + **A** - area

### Other files

1. **UzytkownikXX** (UserXX) - contact details for the Voivodeship Marshal's Office. "XX" contains TERC (voivodeship ID).
2. Files with names: "**Ciek** (Watercourse)", "**LiniaKolejowa** (Railway line)", "**SzlakDrogowy** (Road trail)", "**WezelKolejowy** (Railway junction)", "**ZbiornikWodny** (Reservoir)" contain metadata for these objects.
